Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-10-20 manuscript/manuscript.tex
Edited manuscript

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/linear-D-thin.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thin spherical shell of 1km of thickness with the linear density defined on equation \ref{eq:density-linear}. The computations were performed on the four grids described in Table \ref{tab:grids} and for different values of the distance-size ratio $D$. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-linear-thin}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/linear-D-thick.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thick spherical shell of 35km of thickness with the linear density defined on equation \ref{eq:density-linear}. The computations were performed on the four grids described in Table \ref{tab:grids} and for different values of the distance-size ratio $D$. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-linear-thick}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/exponential-D-thin.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thin spherical shell of 1km of thickness with the exponential density defined on equation \ref{eq:density-exp}. The computations were performed on the four grids described in Table \ref{tab:grids} and for different values of the distance-size ratio $D$. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-exp-thin}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/exponential-D-thick.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thick spherical shell of 35km of thickness with the exponential density defined on equation \ref{eq:density-exp}. The computations were performed on the four grids described in Table \ref{tab:grids} and for different values of the distance-size ratio $D$. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-exp-thick}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/exponential-b-thin.pdf}
\caption{
    Results of the accuracy tests for different exponential density functions in case of a spherical shell of 1km of thickness.
    (a) Density functions used in the tests, each one with a different value of $b$ and normalised in such way that they reaches a density of 2900kg/m$^{3}$ at the bottom of the shell.
    (b) Differences between the Marussi tensor component $g_{zz}$ generated by the numerical model and the analytical solution for each density function. Each computation was performed on the big grid described in Table \ref{tab:grids}, for different values of the distance-size ratio $D$. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-exp-power-thin}
\end{figure}

@@

>>>>

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/linear-D-thin.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thin spherical shell of 1km of thickness with the linear density defined on equation \ref{eq:density-linear}. The computations were performed on the four grids described in Table \ref{tab:grids}, for different values of the distance-size ratio $D$ and without applying the density-based discretization algorithm. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-linear-thin}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/linear-D-thick.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thick spherical shell of 35km of thickness with the linear density defined on equation \ref{eq:density-linear}. The computations were performed on the four grids described in Table \ref{tab:grids}, for different values of the distance-size ratio $D$ and without applying the density-based discretization algorithm. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-linear-thick}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/exponential-D-thin.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thin spherical shell of 1km of thickness with the exponential density defined on equation \ref{eq:density-exp}. The computations were performed on the four grids described in Table \ref{tab:grids}, for different values of the distance-size ratio $D$ and without applying the density-based discretization algorithm. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-exp-thin}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/exponential-D-thick.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thick spherical shell of 35km of thickness with the exponential density defined on equation \ref{eq:density-exp}. The computations were performed on the four grids described in Table \ref{tab:grids}, for different values of the distance-size ratio $D$ and without applying the density-based discretization algorithm. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-exp-thick}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/exponential-b-thin.pdf}
\caption{
    Results of the distance-size ratio determination for different exponential density functions in case of a spherical shell of 1km of thickness.
    (a) Density functions used in the tests, each one with a different value of $b$ and normalised in such way that they reaches a density of 2900kg/m$^{3}$ at the bottom of the shell.
    (b) Differences between the Marussi tensor component $g_{zz}$ generated by the numerical model and the analytical solution for each density function. Each computation was performed on the big grid described in Table \ref{tab:grids}, for different values of the distance-size ratio $D$. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-exp-power-thin}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/exponential-delta-thin.pdf}
\caption{
    Results of the delta ratio determination, applied to a thin spherical shell (1km of thickness) with various exponential density functions, each one with different value of $b$.
    (a) Density functions used to perform the test.
    (b) Differences between the numerical model and the corresponding analytical solution for several values of $\delta$ and $b$.}
\label{fig:exponential-delta-thin}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/exponential-delta-thick.pdf}
\caption{
    Results of the delta ratio determination, applied to a thick spherical shell (35km of thickness) with various exponential density functions, each one with different value of $b$.
    (a) Density functions used to perform the test.
    (b) Differences between the numerical model and the corresponding analytical solution for several values of $\delta$ and $b$.}
\label{fig:exponential-delta-thick}
\end{figure}

On Figures \ref{fig:exponential-delta-thin}a and \ref{fig:exponential-delta-thick}a we can see the exponential density functions used on each test for a thin and thick spherical shell, respectively.
While Figures \ref{fig:exponential-delta-thin}b and \ref{fig:exponential-delta-thin}b show their results.

In the thin shell case we can conclude that a delta equal to 0.3 guarantee an acceptable accuracy under 0.1\% for the entire set of the density functions, while the thick shell case needs at least a delta equal to 0.2.
We will keep the more conservative value of 0.2 as the default value of delta on future computations.
